Deep Probabilistic Models for Camera Geo-Calibration

### 2018-08-03 chapters/introduction/introduction.tex
introduction first para

\begin{chapquote}{Alan Turing}
  ``I propose to consider the question: Can machine think?''
\end{chapquote}

Before the father of computer asked this question, creating
machines that can think as human has been a dream through the human
history. In 1960s, MIT professor Dr. Marvin Minsky asked his
undergraduates to develop programs that can recognize objects from a
scene in their summer project~\cite{boden2006mind}. Half a century has
passed, the question of this ``summer project'' still remains open.

The ultimate goal of image understanding is to transfer the visual
signals (images/videos) into abstract symbolic descriptions of the
world which are helpful for decision making.
In general, understanding images is not trivial for machines.
Under different scenarios, researchers divide image
understanding into different computer vision tasks. For example,
pedestrian detection is essential to autonomous driving, and image
retrieval to an image searching engine.

For many applications, knowing when, where, and in which direction a
picture was taken is important to understand the world. We refer to 
such a vision task as {\em geo-calibration}.
In current work of geo-calibration, most algorithms are
deterministic, which means they output fixed solutions. Deterministic
systems may seem straight-forward but they also have some 
drawbacks: 1) Deterministic systems can not handle uncertainties in
the real world very well. 2) They are not
friendly to graphic model applications.
To address these problems, We propose to build probabilistic models
for camera geo-calibration.

Beside geo-calibration, this thesis also studies the possibilities of
learning high-level image representations with the help of geographic
information. In one of our work, we demonstrate that we are able to
learn geo-temporal feature representations of image with geographic
locations and image timestamps. In another work, we exploit image geographic
locations to transfer the learned knowledge of a CNN for ground image
semantic segmentation to another CNN designed for overhead image
semantic segmentation.

>>>>

\begin{chapquote}{Alan Turing}
  ``I propose to consider the question: Can machine think?''
\end{chapquote}
The ultimate goal of image understanding is to transfer the visual
signals (images/videos) into abstract symbolic descriptions of the
world which are helpful for decision making.
However, understanding images is a not trivial task for machines.
In order to handle various complicated scenarios, researchers divide
image understanding into different computer vision tasks: Pedestrian
detection for autonomous driving, and image retrieval for image
searching engines \etc.

For many applications, knowing when, where, and in which direction a
picture was taken is important to understand the world. We refer to 
estimating these properties as the task of  {\em geo-calibration}.
In current work of geo-calibration, most algorithms are
deterministic, which means they output fixed solutions. Deterministic
systems may seem straight-forward but they also have some obvious
drawbacks: 1) Deterministic systems can not model the inherent
uncertainties from images of ambiguous scenes. 2) They are not
friendly to applications that take probabilistic inputs. To address
these problems, We propose to build probabilistic models for camera
geo-calibration.

Feature engineering is essential for image understanding. In recent
years, learning based approaches for high-level feature construction
like deep neural nets get popular. However, most of these feature
learning methods heavily relies on manually labeled data. In our
thesis, we presented alternative ways to learn high-level image
representations when the manually labeled data is either insufficient
or absent. We show that learning to geo-calibrate a camera is helpful
for high-level feature extracting.

### 2018-08-03 chapters/introduction/junk.tex
minor change
introduction first para

>>>>

%\subsection{Overhead Imagery}
%Overhead imagery plays an import role in the cross-view learning area.
%To construct a cross view image pair, we need to know the geographic
%location (sometimes also with the geographic orientation).
%\todo{rewrite the following} Efforts have been made to
%automate overhead image analysis. As early as
%1970~\cite{idelsohn1970learning} methods were introduced for
%classifying terrain types from a single overhead image, with the goal
%of automatically generating terrain maps.  Similarly, in 1976 Bajcsy
%et al.~\cite{bajcsy1976computer} described a system for recognizing
%roads, intersections, and other road-like objects in overhead imagery.
%However, as overhead imaging differs drastically from ground-level
%imaging, the majority of techniques that have been developed have
%occurred independently and in task-specific ways~\cite{Rozen}.

%Benefited from the fast growing monitoring satellite market, overhead
%imagery grows fast nowadays. Microsoft BingMap provides public access
%to their overhead image database with various resolution options.
%Given the geographic information of the ground image, we are able to
%download the corresponding overhead images to form the geo-orientation
%aligned cross-view image pairs.

Before the father of computer asked this question, creating
machines that can think as human has been a dream through the human
history. In 1960s, MIT professor Dr. Marvin Minsky asked his
undergraduates to develop programs that can recognize objects from a
scene in their summer project~\cite{boden2006mind}. Half a century has
passed, the question of this ``summer project'' still remains open.

%Beside geo-calibration, this thesis also studies the possibilities of
%learning high-level image representations with the help of geographic
%information. In one of our work, we demonstrate that we are able to
%learn geo-temporal feature representations of image with geographic
%locations and image timestamps. In another work, we exploit image geographic
%locations to transfer the learned knowledge of a CNN for ground image
%semantic segmentation to another CNN designed for overhead image
%semantic segmentation.

### 2018-08-03 dissertation.tex
introduction first para

\abstract
{ \SingleSpacing
The ultimate goal of image understanding is to transfer the visual
images into numerical or symbolic descriptions of the world
that are helpful for other thought processes for decision making.
In general, understanding images is not trivial for machines.
Under different scenarios, researchers divide image
understanding into different computer vision tasks. For example,
pedestrian detection is essential to autonomous driving, and image
retrieval to an image searching engine. Knowing when, where, and in
which direction picture was taken, the task of geo-calibration makes
it possible to use imagery to understand the world and how it changes
in time. Current models for geo-calibration are mostly deterministic,
namely they output fixed solutions. However, deterministic 
models can not handle uncertainties in our real life well.
Furthermore, their outputs are not very friendly to graphic model
algorithms. To address these limitations, we propose a probabilistic
model for camera geo-calibration using deep neural networks (DNNs),
providing more flexible inputs. We also demonstrate that the
geographic information is helpful for high-level feature extraction.
The primary contributions of our thesis include building a
probabilistic model for camera geo-calibration, and learning
high-level image representations with help of geographic information.
Our discoveries can provide researchers new insights for both camera
geo-calibration and DNN training.
}
\keywords{geo-calibration, deep neural networks, computer vision}

>>>>

\abstract
{ \SingleSpacing
The ultimate goal of image understanding is to transfer the visual
images into numerical or symbolic descriptions of the world
that are helpful for decision making.
%
%In general, understanding images is not trivial for machines.
%Under different scenarios, researchers divide image
%understanding into different computer vision tasks. For example,
%pedestrian detection is essential to autonomous driving, and image
%retrieval to an image searching engine.
%
Knowing when, where, and in which direction picture was taken, the
task of geo-calibration makes it possible to use imagery to understand
the world and how it changes in time. Current models for
geo-calibration are mostly deterministic, namely they output fixed
solutions. However, deterministic models can not model the
uncertainties that are inherent when the scene of the image is ambiguous.
Furthermore, their outputs are not very friendly to algorithms that
take probabilistic inputs. To address these limitations, we
propose a probabilistic model for camera geo-calibration using deep
neural networks.
%
While our primary contribution is geo-calibration, We also show that
learning to geo-calibrate a camera is helpful for high-level feature
extraction.
%
%Our discoveries can provide researchers new insights for both camera
%geo-calibration and DNN training.
}
\keywords{computer vision, geo-calibration, deep neural networks}
